Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-26 paper.tex
Update on Overleaf.

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants}
\label{fig:start}
\end{figure}

>>>>

We demonstrate the main advantage of \ctr~over the older \ttctr~ in the Figure~\ref{fig:start}.

\begin{figure}[hbt!]
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/start.eps}
\vspace{-12pt}
\caption{\footnotesize (a)}
\vspace{-12pt}
\end{subfigure}%
\begin{subfigure}{0.5\linewidth}
\includegraphics[width=\linewidth]{experiments/end.eps}
\vspace{-12pt}
\caption{\footnotesize (b)}
\vspace{-12pt}
\end{subfigure}
\caption{Comparison of \texttt{start\_X$_{LT}$} (a) and \texttt{end\_X$_{LT}$} (b) queries, with all variants. Note that the logarithmic scale for the y axis in (b)}
\label{fig:start}
\end{figure}
